Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip0.tex
Try to push a working version
Update triangle ineq. to not use q norm

If
\begin{align}
    &\norm{D_1 - D_2}_q \leq \eps   \\
    &\norm{D_4 - D_6}_q \leq \eps',
\end{align}
then
\begin{align}
   \norm{ D_3 - D_5}_q \leq \eps+\eps'
\end{align}
\end{lem}
% \begin{align}
%     D_1 &\approx_{q,\eps} D_2 \\
%     D_4 &\approx_{q,\eps'} D_6,
% \end{align}
% then
% \begin{align}
%     D_3 \approx_{q,\eps+\eps'} D_5
% \end{align}
\begin{proof}
% Since
% $$\norm{D_4 - D_6}_q \leq \eps',$$
% there exist

We prove by contradiction. Suppose that
$$\norm{ D_3 - D_5}_q > \eps+\eps',$$
$$D_3\not\approx_{c, \eps+\eps'} D_5,$$
then there exist a quantum circuit $A$ of size $poly(n)$ such that
$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that
$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$
$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$
So
\begin{align}
    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
     > &\eps
\end{align}
This contradicts with the assumption that $\norm{D_1 - D_2}_q \leq \eps $.
\end{proof}

@@

By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability.
\end{proof}

>>>>

If
\begin{align}
	D_1\approx_{c,\eps} D_2 \\
	D_4\approx_{c,\eps'} D_6,
\end{align}
then
\begin{align}
	D_3\approx_{c,\eps+\eps'} D_5
\end{align}
\end{lem}
% \begin{align}
%     D_1 &\approx_{q,\eps} D_2 \\
%     D_4 &\approx_{q,\eps'} D_6,
% \end{align}
% then
% \begin{align}
%     D_3 \approx_{q,\eps+\eps'} D_5
% \end{align}
\begin{proof}
% Since
% $$\norm{D_4 - D_6}_q \leq \eps',$$
% there exist

We prove by contradiction. Suppose that
$$D_3\not\approx_{c, \eps+\eps'} D_5,$$
then there exist a quantum circuit $A$ of size $poly(n)$ such that
$$\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| > \eps+\eps'.$$
Since $$\norm{D_4 - D_6}_q \leq \eps'$$, we know that
$$\L\|\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \leq \eps'.$$
Since $D_1=D_3+D_4$ and $D_2=D_5+D_6$, we have that
$$ \Pr[A({D_1})=1]= \Pr[A({D_3})=1]+ \Pr[A({D_4})=1]$$
$$ \Pr[A({D_2})=1]= \Pr[A({D_5})=1]+ \Pr[A({D_6})=1].$$
So
\begin{align}
    &\L\|\Pr[A({D_1})=1]-\Pr[A({D_2})=1]  \R\| \nn \\
    =&   \L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1] +\Pr[A({D_4})=1]-\Pr[A({D_6})=1]  \R\| \nn \\
    \geq  &\L\|\Pr[A({D_3})=1]-\Pr[A({D_5})=1]  \R\| - \L\|\Pr[A({D_6})=1]-\Pr[A({D_4})=1]  \R\|  \nn \\
     > &\eps
\end{align}
	This contradicts with the assumption that $D_1\approx_{c,\eps}D_2$.
\end{proof}

@@

By Fact~\ref{fact:perfectly_pass_test} and the assumption of the lemma, $p_{alt}$ passes the testing round with $(1-\negl(\lambda)$ probability. Therefore by Lemma~\ref{lem:urmila-binding}, there exist a state $\rho_{alt}$ such that
